\chapter{Referências}
[1] TECHTUDO. O que é chip UWB: entenda a nova aposta da Apple e Samsung. Disponível em: https://www.techtudo.com.br/noticias/2020/08/o-que-e-chip-uwb-entenda-a-nova-aposta-da-apple-e-samsung.ghtml. Acesso em: 02, outubro, 2020.

[2] ELETRONIC DESIGN. What’s The Difference Between Measuring Location By UWB, Wi-Fi, and Bluetooth?. Disponível em: https:https://www.electronicdesign.com/technologies
/communications/article/21800581/whats-the-difference-between-measuring-location-by-uwb-wifi-and-bluetooth. Acesso em: 02, outubro, 2020.

[3] BLEESK. Ultra-Wideband (UWB). Disponível em: https://bleesk.com/uwb.html. Acesso em: 02, outubro, 2020.

[4] ELIKO. The Story Behind UWB Technology and Indoor Positioning. Disponível em: https://www.eliko.ee/uwb-technology-indoor-positioning/. Acesso em: 02, outubro, 2020.

[5] Amsters, R. and Demeester, E. and Slaets, P. and Stevens, N. and Lauwers, Q. (2019). Evaluation of Low-Cost / High-Accuracy Indoor Positioning Systems. ALLSENSORS 2019: The Fourth International Conference on Advances in Sensors, Actuators, Metering and Sensing Evaluation, (c), 15–20.

[6] COMO a Bonduelle melhorou a eficiência do seu armazém em 3\%. Pozyx. Disponível em: https://www.pozyx.io/bonduelle-case-study. Acesso em: 01, outubro, 2020.

[7] M. Ridolfi et al., “Experimental evaluation of uwb indoor positioning for sport postures,” Sensors (Switzerland), vol. 18, no. 1, 2018, pp. 1–20.Experimental Evaluation of UWB Indoor Positioning for Sport Postures